Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-11-23 Scripts/Initial_Analysis.Rmd
FIxed missing siland nations of Fig S4A

World_map <- rnaturalearth::ne_countries(scale = 'small', returnclass = c("sf")) %>%
  clean_names() %>% 
  select(iso_a3,sovereignt,sov_a3,name,name_long,region_wb,continent,geometry) %>% 
  st_transform(crs = "+proj=eck4") %>%
  # st_transform(crs = 4326) %>% # 4326
  mutate(iso_a3 = ifelse(sovereignt == "Norway","NOR",
                         ifelse(name == "France","FRA",
                                iso_a3)
                         )
         ) %>% 
    left_join(World_map_dat,
            by = "iso_a3")

@@

# ggplot(Eez_centroid_sf) +
#   geom_sf() +
#   geom_sf(data = World_map, aes(), fill = "grey") +
#   geom_sf(data = World_eez_sf, aes(), fill = "white")

@@

@@

land_map <- ggplot(World_map_part) +
  geom_sf(aes(fill = participation-2000),
          color =  "white",
          size = 0.1
  ) +
  geom_sf(data = no_toe_land, aes(fill = as.numeric(value)),
          color =  "white",
          size = 0.1) +
  scale_fill_viridis("Transboundary fish revenue (%)",
                     limits = c(0,100),
                     breaks = seq(0,100,25),
                     labels = seq(0,100,25),
                     direction = 1,
                     na.value = "lightblue",
                     option = "A"
  ) +
  my_ggtheme_m(leg_pos = "bottom") +
  theme(legend.key.width = unit(3, "line")) +
  guides(
    fill=guide_colorbar(title.position="top", 
                        title.hjust =0.5)
  )

@@

>>>>

World_map <- rnaturalearth::ne_countries(scale = 'large', returnclass = c("sf")) %>%
  clean_names() %>% 
  select(iso_a3,sovereignt,sov_a3,name,name_long,region_wb,continent,geometry) %>% 
  st_transform(crs = "+proj=eck4") %>%
  # st_transform(crs = 4326) %>% # 4326
  mutate(iso_a3 = ifelse(sovereignt == "Norway","NOR",
                         ifelse(name == "France","FRA",
                                iso_a3)
  )
  ) %>% 
  left_join(World_map_dat,
            by = "iso_a3")

@@

@@

centroid_map <- ggplot() +
  geom_sf(data = World_eez_sf, aes()) +
  geom_sf(data = subset(World_map, !sovereignt %in% c("Antarctica")), aes(),fill = "grey90") +
  geom_sf(data = Eez_centroid_sf, aes()) +
  my_ggtheme_m(leg_pos = "")

ggsave(
  plot = centroid_map,
  "./Figures/centroid_map.png",
  width = 8,
  height = 5,
  units = "in"
)

@@

land_map <- ggplot() +
  geom_sf(data = World_map_part,
          aes(fill = participation-2000, 
              color = participation-2000),
          size = 0.1
  )  +
  geom_sf(data = no_toe_land, aes(fill = as.numeric(value),
                                  color = as.numeric(value)),
          size = 0.1) +
  scale_fill_viridis("Transboundary fish revenue (%)",
                     limits = c(0,100),
                     breaks = seq(0,100,25),
                     labels = seq(0,100,25),
                     direction = 1,
                     na.value = "lightblue",
                     option = "A"
  ) +
  scale_color_viridis("Transboundary fish revenue (%)",
                      limits = c(0,100),
                      breaks = seq(0,100,25),
                      labels = seq(0,100,25),
                      direction = 1,
                      na.value = "lightblue",
                      option = "A"
  ) +
  my_ggtheme_m(leg_pos = "bottom") +
  theme(legend.key.width = unit(3, "line")) +
  guides(
    fill=guide_colorbar(title.position="top",
                        title.hjust =0.5)
  )

@@

ggplot() +
  geom_sf(data = rnaturalearth::ne_countries(scale = 'large', returnclass = c("sf")),aes())
